Meta-analysis

### 2020-01-02 05_MetaAnalysis.Rmd
code checks and meta_contrasts

library(RColorBrewer)
library(tidyverse)
library(theme.usq)
library(bomrang)
library(lme4)

@@

We will evaluate wheather the imputed variances confer a significant difference to the recorded means. I created a distance matrix of two standard errors above the mean against two standard errors below the mean. If any errors don't overlap, infering signicifant difference, the imputed variances are discarded and resampled until all treatment variances show no significant differences.

```{r imputing_variances}

@@

```{r imputing_MSE}
hist(unique(slimmer_PM_dat$Y_Msquare))
hist(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution

@@

for(i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`),]$trial_ref){
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i,"Y_Msquare"] <- 
      exp(
         rnorm(n = 1,
               mean = mean(TrialMSQ$`unique(Y_Msquare)`, na.rm = TRUE),
               sd(TrialMSQ$`unique(Y_Msquare)`, na.rm = TRUE)
         )
      )
   }

@@

```{r meta_1}
library(metafor)

slimmer_PM_dat$yi <- slimmer_PM_dat$grain_yield.t.ha
slimmer_PM_dat$vi <- slimmer_PM_dat$Y_Msquare/(slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha^2)

slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management)
table(slimmer_PM_dat$spray_management)

@@

```{r inspect_for_outliers}
head(slimmer_PM_dat)

slimmer_PM_dat %>%
#   filter(spray_management == "Late_plus") %>%
   ggplot(aes(prop_yield_gain, fill = spray_management))+
   geom_histogram(alpha = 0.5)

slimmer_PM_dat %>%
   filter(spray_management == "Late_plus") %>%
   ggplot(aes(prop_yield_gain, fill = trial_ref))+
   geom_histogram(alpha = 0.5)

slimmer_PM_dat %>%
   filter(spray_management == "Recommended") %>%
   ggplot(aes(prop_yield_gain, fill = trial_ref))+
   geom_histogram(alpha = 0.5)

@@

>>>>

library(RColorBrewer)
library(tidyverse)
library(theme.usq)
library(bomrang)
library(lme4)
library(kableExtra)

@@

We will evaluate wheather the imputed variances confer a significant difference to the recorded means. I created a distance matrix of two standard errors above the mean against two standard errors below the mean. If any errors don't overlap, infering signicifant difference, the imputed variances are discarded and resampled until all treatment variances show no significant differences.
### Imputing sample variances
```{r imputing_variances}

@@

#### Imputing sample variances from Mean squares
```{r imputing_MSE}
slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
hist(unique(slimmer_PM_dat$Y_Msquare))
hist(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution

@@

for(i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`),]$trial_ref){
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i,"Y_Msquare"] <- 
      exp(
         rnorm(n = 1,
               mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
               sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
         )
      )
   }

@@

Before plotting lets have a look at how the trimmed down, modified data looks.

```{r treatment_means_plot}
slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management, levels(slimmer_PM_dat$spray_management)[rev(c(1,2,4,5,3))])

slimmer_PM_dat %>%
   ggplot(aes(y = prop_yield_gain, x = spray_management))+
   geom_boxplot()+
   #geom_point(position = "jitter", alpha = 1/5)+
   geom_jitter(width = 0.1, alpha = 1/5)+
   theme_usq()+
   labs(x = "Spray management variable", 
        y = "Grain yield (t/Ha)",
        title = "Mean grain yield from each treatment \n categorised by spray management scenario")+
   theme(plot.title = element_text(hjust = 0.5))+
   coord_flip()

kableExtra::kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year), align=rep('c', 8))%>%  #commented as was redering empty, needs a look in
   kable_styling("striped", fixed_thead = TRUE, full_width = FALSE, position = "center")

## Meta-analysis
```{r meta_1}
library(metafor)
slimmer_PM_dat$spray_management <-
   factor(slimmer_PM_dat$spray_management,levels(slimmer_PM_dat$spray_management)[c(2,3,1,4,5)])

slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha)
slimmer_PM_dat$vi <- slimmer_PM_dat$Y_Msquare/(slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha^2)

slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management)
slimmer_PM_dat$trial_ref <- factor(slimmer_PM_dat$trial_ref)
slimmer_PM_dat$trial <- factor(slimmer_PM_dat$trial)

@@

```{r compare_meta&lmer}
lme_PM <- lmer(yi ~ spray_management + (spray_management | trial), data = slimmer_PM_dat)

summary(lme_PM)

@@

```{r meta_contrasts}
anova(PM_mv_AI, L=rbind(c(0,1,-1,0,0),  # early vs late plus
                        c(0,1,0,-1,0),  # early vs recommended
                        c(0,1,0,0,-1),  # early vs recommended plus
                        c(0,0,-1,1,0),  # late plus vs recommended 
                        c(0,0,-1,0,1),  # late plus vs recommended  Plus
                        c(0,0,0,-1,1))) # recommended vs recommended plus
```
Results show that Early applications are not significantly different to the no spray control or the one and two spray management options at the recommended time. Lets view this on a plot.

```{r meta_results}
results_AI <- data.frame(cbind(exp(PM_mv_AI$b), 
                              exp((PM_mv_AI$ci.lb)),
                              exp(PM_mv_AI$ci.ub)))

results_AI <- data.frame(cbind(PM_mv_AI$b, 
                              (PM_mv_AI$ci.lb),
                              PM_mv_AI$ci.ub))

treat <- c("control", "Early", "Recommended", "Recommended_plus","Late_plus")
efficacy <- tbl_df(results_AI)
efficacy$treat <- treat
efficacy$se <- PM_mv_AI$se
colnames(efficacy) <- c("Mean", "CIsup", "CIinf", "Treatment", "SE")
efficacy
```

```{r meta_plot}
efficacy %>% 
  ggplot(aes(Treatment, Mean))+
  geom_point(aes(size=1/SE), shape=15)+
  geom_linerange(aes(ymin = CIinf, ymax = CIsup))+
  coord_flip()+
  theme_grey()+
   geom_hline(yintercept = efficacy[efficacy$Treatment == "control",]$CIinf)

Check the yeild

```{r}
boxplot(slimmer_PM_dat$grain_yield.t.ha ~ slimmer_PM_dat$spray_management)
